### 2022-02-24 about/vita.tex
Added manderz
New semester
Lots of new links

\def\up#1{\leavevmode \raise.16ex\hbox{#1}}
\def\sectheader#1{{\bigskip\elevensc #1}\smallskip\hrule\medskip}
\def\leftright#1#2{{#1}\hfill{#2}\par}
\def\CEE{{\mc C}}
\def\UNIX{{\mc UNIX}}
\def\thing{\item{$\bullet$}}

@@

\leftright{\bf M.Sc.\ Mathematics}{\bf May 2021 -- present}
\leftright{\sl McGill University}{\sl Montr\'eal, QC, Canada}
\smallskip
Supervisor: Luc Devroye.
\medbreak
\leftright{\bf B.Sc.\ Joint Honours Mathematics and Computer Science}{\bf September 2017 -- April 2021}
\leftright{\sl McGill University}{\sl Montr\'eal, QC, Canada}
\smallskip
Minor: Linguistics. CGPA: 3.84/4.
\medbreak
\leftright{\bf Exchange semester}{\bf February -- June 2019}
\leftright{\sl Faculty of Mathematics and Physics, Charles University}{\sl Prague, Czech Republic}
\smallskip
Grade: 1 on all courses (highest score attainable).

@@

Analysis of random discrete structures, analysis and design of algorithms, enumerative combinatorics,
additive combinatorics, algebra.

@@

\papercount=2
\pubbegin P
\papitem (with Anna M. Brandenberger and Luc Devroye)
Root estimation in Galton--Watson trees. To appear in {\sl Random Structures and Algorithms}, 24~pp.
[arXiv:2007.05681]
\papitem (with Rosie Y. Zhao)
Arithmetic subsequences in a random ordering of an additive set.
{\sl Integers: Electronic Journal of Combinatorial Number Theory} {\bf 21} (2021), \#A89, 19~pp.
[arXiv:2012.12339]

@@

\begingroup\parindent=10pt
\thing (with Luc Devroye and Rosie Y. Zhao)
The independence number of a Bienaym\'e--Galton--Watson tree
and related parameters. {\sl arXiv preprint 2106.14389}, 20~pp.
\smallskip
\thing (with Jad Hamdan and Jonah Saks)
The lattice of arithmetic progressions. {\sl arXiv preprint 2106.05949}, 15~pp.
\smallskip
\thing (with Anna M. Brandenberger, Luc Devroye, and Rosie Y. Zhao)
Leaf multiplicity in a Bienaym\'e--Galton--Watson tree. {\sl arXiv preprint 2105.12046}, 11~pp.
\endgroup

@@

\sectheader{Work and Volunteer Experience}

\leftright{\bf Teaching assistant}{\bf September 2021 -- present}
\leftright{\sl School of Computer Science, McGill University}{\sl Montr\'eal, QC, Canada}
\smallskip
Teaching assistant for COMP 690, a graduate-level course on the probabilistic analysis of algorithms.
Hold office hours twice a week and responsible for grading of assignments.
\medbreak

\leftright{\bf First responder}{\bf October 2017 -- present}
\leftright{\sl McGill Student Emergency Response Team}{\sl Montr\'eal, QC, Canada}
\smallskip
On call on a weekly basis to provide emergency medical care at campus residences overnight as well as at
university events such as frosh, sports games, and formals. Attend team training sessions twice a month to keep
first-aid skills up-to-date. Most recent first responder certification: September 2020.
\medbreak

\leftright{\bf Grader}{\bf September 2019 -- April 2021}
\leftright{\sl Department of Mathematics and Statistics, McGill University}{\sl Montr\'eal, QC, Canada}
\smallskip
Grading of assignments in the following courses:
\begingroup\parindent=10pt
\smallskip
\thing Winter 2021: MATH 457 Honours Algebra 4
\smallskip
\thing Fall 2020: MATH 323 Probability, MATH 456 Honours Algebra 3
\smallskip
\thing Winter 2020: MATH 240 Discrete Structures
\smallskip
\thing Fall 2019: MATH 235 Algebra 1
\endgroup
\medbreak

\leftright{\bf Helpdesk tutor}{\bf September 2018 -- April 2021}
\leftright{\sl Computer Science Undergraduate Society Helpdesk}{\sl Montr\'eal, QC, Canada}
\smallskip
Hold twice-weekly office hours to tutor students in a variety of undergraduate courses.
Topics covered include elementary data structures and algorithms, command-line scripting,
and functional programming. Recipient of the Tomlinson Engagement Award for Mentoring.
\medbreak

@@

\leftright{\bf Painter}{\bf May -- August 2018}
\leftright{\sl Bakir Contracting Corp.}{\sl Edmonton, AB, Canada}
\smallskip
Exterior painting (siding, decks, fences, trim, etc.) for residential clients.
\medbreak

\leftright{\bf Infantryman}{\bf August 2015 -- August 2017}
\leftright{\sl Singapore Armed Forces}{\sl Singapore}
\smallskip
Held appointment of machine-gun team commander in the 3rd Battalion, Singapore Infantry Regiment.
Led a six-person team consisting of a medic, signaller, sensor, and two-machine gunners within a rifle platoon.
\medbreak

\leftright{\bf Tutor}{\bf September 2014 -- June 2015}
\leftright{\sl \'Ecole Secondaire Beaumont Composite High School}{\sl Beaumont, AB, Canada}
\smallskip
Tutored various students in grades 4 through 11 in chemistry, physics, math, and French.
\medbreak

\leftright{\bf Summer camp counsellor}{\bf June -- August 2014}
\leftright{\sl YoWoChAs Outdoor Education Centre}{\sl Fallis, AB, Canada}
\smallskip
Led children aged 4--15 through various activities (e.g. archery, canoeing, zipline) at a sleepaway camp.
\medbreak

>>>>

\def\up#1{\leavevmode \raise.16ex\hbox{#1}}
\def\sectheader#1{{\bigskip\elevensc #1}\smallskip\hrule\medskip}
\def\leftright#1#2{\hbox to\hsize{{#1}\hfill{#2}}\par}
\def\starleftright#1#2{\hbox to\hsize{\llap{*}{#1}\hfil{#2}}\par}
\def\CEE{{\mc C}}
\def\UNIX{{\mc UNIX}}
\def\thing{\item{$\bullet$}}

@@

\leftright{\bf M.Sc.\ Mathematics}{\bf May 2021 -- present}
\leftright{\sl McGill University}{\sl Montr\'eal, QC, Canada}
\smallskip
Supervisor: Luc Devroye. CGPA: 4.00/4. Thesis topic: ``Structural properties of Galton--Watson trees.''
\medbreak
\leftright{\bf B.Sc.\ Joint Honours Mathematics and Computer Science}{\bf September 2017 -- April 2021}
\leftright{\sl McGill University}{\sl Montr\'eal, QC, Canada}
\smallskip
Minor: Linguistics. CGPA: 3.84/4.
\medbreak
\leftright{\bf Exchange semester}{\bf February -- June 2019}
\leftright{\sl Faculty of Mathematics and Physics, Charles University}{\sl Prague, Czech Republic}
\smallskip
Grade: 1 on all courses (highest score attainable).

@@

Analysis of random discrete structures, analysis and design of algorithms, enumerative combinatorics,
additive combinatorics.

@@

\papercount=3
\pubbegin P
\papitem (with Anna M. Brandenberger, Luc Devroye, and Rosie Y. Zhao)
Leaf multiplicity in a Bienaym\'e--Galton--Watson tree. To appear in {\sl Discrete Mathematics
and Theoretical Computer Science}, 11~pp. [arXiv:2105.12046]
\papitem (with Anna M. Brandenberger and Luc Devroye)
Root estimation in Galton--Watson trees. To appear in {\sl Random Structures and Algorithms}, 24~pp.
[arXiv:2007.05681]
\papitem (with Rosie Y. Zhao)
Arithmetic subsequences in a random ordering of an additive set.
{\sl Integers: Electronic Journal of Combinatorial Number Theory} {\bf 21} (2021), \#A89, 19~pp.
[arXiv:2012.12339]

@@

\begingroup\parindent=10pt
\thing (with Luc Devroye and Rosie Y. Zhao)
The independence number of a Bienaym\'e--Galton--Watson tree
and related parameters. {\sl arXiv preprint 2106.14389}, 20~pp.
\smallskip
\thing (with Jad Hamdan and Jonah Saks)
The lattice of arithmetic progressions. {\sl arXiv preprint 2106.05949}, 15~pp.
\endgroup

@@

\sectheader{Work and Volunteer Experience {\rm($*$ indicates a paid position)}}

\leftright{\bf Mentor}{\bf January 2021 -- present}
\leftright{\bf Department of Mathematics and Statistics, McGill University}{\sl Montr\'eal, QC, Canada}
\smallskip
Meet with two undergraduate students as part of the Directed Reading Program
on a weekly basis to give them an introduction to research-level
mathematics in a casual setting. Focused on topics in extremal combinatorics related to the increasing
triples problem.
\medbreak

\starleftright{\bf Teaching assistant}{\bf September -- December 2021}
\leftright{\sl School of Computer Science, McGill University}{\sl Montr\'eal, QC, Canada}
\smallskip
Teaching assistant for COMP 690, a graduate-level course on the probabilistic analysis of algorithms.
Hold office hours twice a week and responsible for grading of assignments.
\medbreak

\leftright{\bf First responder}{\bf October 2017 -- September 2021}
\leftright{\sl McGill Student Emergency Response Team}{\sl Montr\'eal, QC, Canada}
\smallskip
On call on a weekly basis to provide emergency medical care at campus residences overnight as well as at
university events such as frosh, sports games, and formals. Attend team training sessions twice a month to keep
first-aid skills up-to-date. Most recent first responder certification: September 2020.
\medbreak

\starleftright{\bf Grader}{\bf September 2019 -- April 2021}
\leftright{\sl Department of Mathematics and Statistics, McGill University}{\sl Montr\'eal, QC, Canada}
\smallskip
Grading of assignments in the following courses:
\begingroup\parindent=10pt
\smallskip
\thing Winter 2021: MATH 457 Honours Algebra 4
\smallskip
\thing Fall 2020: MATH 323 Probability, MATH 456 Honours Algebra 3
\smallskip
\thing Winter 2020: MATH 240 Discrete Structures
\smallskip
\thing Fall 2019: MATH 235 Algebra 1
\endgroup
\medbreak

\starleftright{\bf Helpdesk tutor}{\bf September 2018 -- April 2021}
\leftright{\sl Computer Science Undergraduate Society Helpdesk}{\sl Montr\'eal, QC, Canada}
\smallskip
Hold twice-weekly office hours to tutor students in a variety of undergraduate courses.
Topics covered include elementary data structures and algorithms, command-line scripting,
and functional programming. Recipient of the Tomlinson Engagement Award for Mentoring.
\medbreak

@@

\starleftright{\bf Painter}{\bf May -- August 2018}
\leftright{\sl Bakir Contracting Corp.}{\sl Edmonton, AB, Canada}
\smallskip
Exterior painting (siding, decks, fences, trim, etc.) for residential clients.
\medbreak

\starleftright{\bf Infantryman}{\bf August 2015 -- August 2017}
\leftright{\sl Singapore Armed Forces}{\sl Singapore}
\smallskip
Held appointment of machine-gun team commander in the 3rd Battalion, Singapore Infantry Regiment.
Led a six-person team consisting of a medic, signaller, sensor, and two-machine gunners within a rifle platoon.
\medbreak

\starleftright{\bf Tutor}{\bf September 2014 -- June 2015}
\leftright{\sl \'Ecole Secondaire Beaumont Composite High School}{\sl Beaumont, AB, Canada}
\smallskip
Tutored various students in grades 4 through 11 in chemistry, physics, math, and French.
\medbreak

\starleftright{\bf Summer camp counsellor}{\bf June -- August 2014}
\leftright{\sl YoWoChAs Outdoor Education Centre}{\sl Fallis, AB, Canada}
\smallskip
Led children aged 4--15 through various activities (e.g. archery, canoeing, zipline) at a sleepaway camp.
\medbreak
